Effects of Different Pain Relievers and Dosages on Cognitive Retention

### 2025-02-27 paper/EDA.qmd
Adding plots

library(tidyverse)
library(janitor)
library(here)
library(lubridate)
library(arrow)
library(dplyr)
library(knitr)
library(performance)

@@

@@

library(kableExtra)

@@

library(ggplot2)
library(patchwork)  # For combining plots

# Capitalize legend labels
clean_data$drug <- factor(clean_data$drug, labels = c("Aspirin", "Paracetamol", "Placebo", "Tramadol"))

# Create first boxplot
p1 <- ggplot(clean_data, aes(x = drug, y = game_before, fill = drug)) + 
  geom_boxplot() +
  labs(title = "Game Scores Before Treatment", x = "Drug Type", y = "Game Score", fill = "Drug") +
  theme_minimal()

# Create second boxplot
p2 <- ggplot(clean_data, aes(x = drug, y = game_after, fill = drug)) + 
  geom_boxplot() +
  labs(title = "Game Scores After Treatment", x = "Drug Type", y = "Game Score", fill = "Drug") +
  theme_minimal()

# Combine both plots with a single caption
p1 / p2 + plot_annotation()

>>>>

library(tidyverse)
library(janitor)
library(here)
library(lubridate)
library(arrow)
library(dplyr)
library(knitr)
library(performance)
library(kableExtra)

@@

clean_data$improvement <- clean_data$game_after - clean_data$game_before

improvement_summary <- clean_data %>%
  group_by(drug) %>%
  summarise(
    Mean_Improvement = mean(improvement, na.rm = TRUE),
    SD_Improvement = sd(improvement, na.rm = TRUE),
    Median_Improvement = median(improvement, na.rm = TRUE)
  )

kable(improvement_summary, format = "latex", booktabs = TRUE, caption = "Mean Improvement in Game Scores by Drug")

@@

@@

library(ggplot2)
library(patchwork)

#References
#https://r-graph-gallery.com/package/patchwork.html

clean_data$drug <- factor(clean_data$drug, labels = c("Aspirin", "Paracetamol", "Placebo", "Tramadol"))

# Create first boxplot
p1 <- ggplot(clean_data, aes(x = drug, y = game_before, fill = drug)) + 
  geom_boxplot() +
  labs(title = "Memory Game Scores Before Treatment", x = "Drug Type", y = "Game Score", fill = "Drug") +
  theme_minimal()

# Create second boxplot
p2 <- ggplot(clean_data, aes(x = drug, y = game_after, fill = drug)) + 
  geom_boxplot() +
  labs(title = "Memory Game Scores After Treatment", x = "Drug Type", y = "Game Score", fill = "Drug") +
  theme_minimal()

p1 / p2 + plot_annotation()

```{r}
#| echo: false
#| warning: false
#| message: false
#| fig.width: 9
#| fig.height: 8
#| dpi: 300
#| fig-cap: "Boxplot of Memory Card Scores Before and After by Drug"

library(ggplot2)
library(patchwork)

clean_data$drug <- factor(clean_data$drug, labels = c("Aspirin", "Paracetamol", "Placebo", "Tramadol"))

p1 <- ggplot(clean_data, aes(x = drug, y = cards_before, fill = drug)) + 
  geom_boxplot() +
  labs(title = "Memory Card Scores Before Treatment", x = "Drug Type", y = "Memory Card Score", fill = "Drug") +
  theme_minimal()

p2 <- ggplot(clean_data, aes(x = drug, y = cards_after, fill = drug)) + 
  geom_boxplot() +
  labs(title = "Memory Card Scores After Treatment", x = "Drug Type", y = "Memory Card Score", fill = "Drug") +
  theme_minimal()

p1 / p2 + plot_annotation()

```{r}
#| echo: false
#| warning: false
#| message: false
#| fig.width: 7
#| fig.height: 4
#| dpi: 300
#| fig-cap: "Distribution of Dosage Levels"

ggplot(clean_data, aes(x = dosage_level, fill = dosage_level)) +
  geom_bar() +
  labs(title = "Distribution of Dosage Levels", x = "Dosage Level", y = "Count") +
  theme_minimal()
